Analysis

### 2023-03-28 Analysis.rmd
update expert table

expert_scores_summarised <- expert_ensemble$scores |>
  filter(scale %in% c("log", "natural")) |>
  summarise_scores(by = c("model", "target_type", "scale", "horizon", "forecast_date")) |>
  group_by(target_type, scale, horizon) |>
  # mutate(interval_score = (interval_score - mean(interval_score)) / sd(interval_score)) |>
  group_by(model, target_type, scale, horizon) |>
  summarise(mean = mean(interval_score), 
            sd = sd(interval_score)) |>
  pivot_wider(id_cols = c(model, target_type, horizon), 
              names_from = scale, values_from = c(mean, sd), names_prefix = "stand_") |>
  arrange(target_type, model)

@@

expert_ensemble$scores |>
  rbind(filter(scores, model == "EuroCOVIDhub-ensemble"), fill = TRUE) |>
   make_performance_table(
     model_filter = c("Expert", "Non-Expert", "EuroCOVIDhub-ensemble"),
     cap = "Performance for four-week-ahead forecasts of experts and non-experts. Values have been cut to three significant digits and rounded. \\label{tab:scores-experts-4}"
    ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-experts-4.tex')

>>>>

@@

expert_ensemble$scores |>
  rbind(filter(scores, model == "crowd-ensemble"), fill = TRUE) |>
   make_performance_table(
     model_filter = c("Expert", "Non-Expert", "crowd-ensemble"),
     baseline = "crowd-ensemble",
     hor = 4,
     cap = "Performance for four-week-ahead forecasts of experts and non-experts. Values have been cut to three significant digits and rounded. \\label{tab:scores-experts-4}"
    ) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-experts-4.tex')
